Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-12 analysis/report/effectiveness_report.Rmd
fix dual timescales by only including date of vaccination as a baseline covariate in the vaccination timescale models.
calendar-time PLR models still probably wrong!

* On the *treatment time-scale*, time zero is the date of vaccination. Calendar-time is included as an additional covariate, in weekly intervals, using restricted cubic spline with knots at the first and second tertile, plus boundary knots. Here, follow-up time is stratified into weekly intervals with the vaccine-specific effect estimated within each time-strata. In `R`'s `coxph` function, this is modelled using `vaccine_type:strata(week_since_first_dose)`.

>>>>

* On the *treatment time-scale*, time zero is the date of vaccination. Date of vaccination is included as an additional baseline covariate using a restricted cubic spline with knots at the first and second tertile, plus boundary knots. Here, follow-up time is stratified into weekly intervals with the vaccine-specific effect estimated within each time-strata. In `R`'s `coxph` function, this is modelled using `vaccine_type:strata(week_since_first_dose)`.
